### 2018-06-03 MSc_Marko_Docevski_tekst.tex
Updates from ShareLaTeX

\cite{GarciaSalas2011} Glorified n-gram/Markov chain model with the Frequency matrix, in combination with a Time matrix per piece that they use to generate music...
They have a aggregate Frequency matrix, but that's about it. Definition 14: Probability Matrix (PM) is a matrix with n rows and n columns. The algorithm to generate probability matrix PM is PMi,j = FDMi,j/Ti
In literature, several problems for developing models for fine arts, especially music have been noted. Some of them are: How to evaluate the results of a music generator? How to determine if what such a system produces is music or not? How to say if a music generator system is better than other? Can a machine model expressivity? Different methods have been used to develop music composition systems, for example: noise [5], cellular automata [20], grammars [13, 22], evolutionary methods [13], fractals [14, 16], genetic algorithms [1], case based reasoning [19], agents [21] and neural networks [7, 15]. Some systems are called hybrid since they combine some of these techniques. For a comprehensive study please refer to [23] and [17]. Musical Evolutionary system: Corpus fed to a learning function. The learning function outputs learned rules. The composing function uses the rules and a user request to generate music, and it feeds back to the leanring function. The learning rules are unsupervised. The function L is a learning process that generates rules from each musical composition mi creating a representation of musical knowledge. The evolutionary system originally does not have any rule. These learned rules K are used to generate musical composition m automatically. For listening of the new music composition there is a function I called musical interpreter or performer that generates the sound. A musical composition is a structure of note sequences made of other structures built over time. How many times a musical note is used after another reflects patterns of sequences of notes that characterizes a genre, style or an author of a musical composition. We focus on finding patterns on monophonic music. Our model is based on a linguistic approach [9]. We describe musical compositions as phrases made up of sequences of notes as lexical items that represent sounds and silences throughout time. The set of all musical compositions forms the musical language. In the following paragraphs we define some basic concepts that we will use in the rest of this paper. To represent rules K we use matrices for musical frequencies and for musical times. We refer to them as rules M. Originally these matrices are empty; they are modified with every musical example. Rules M are divided by function L into MF and MT where MF is the component of musical frequencies (mf) rules extracted from musical compositions and MT is the component of musical time (mt) rules. MF is a workspace formed by two matrices. One of them is a frequency distribution matrix (FDM) and the other one is a cumulative frequency distribution matrix (CFM). Each time a musical composition mi arrives, L upgrades FDM. Then it recalculates CFM. Monophonic music composition is the art of creating a single melodic line with no accompaniment. To compose a melody a human composer uses his/her creativity and musical knowledge. In our model composer function C generates a melodic line based on knowledge represented by cumulative frequency distribution matrix CFM. Probability Matrix (PM) is a matrix with n rows and n columns. The algorithm to generate probability matrix PM is: ∀i ∈ [1,n], ∀j ∈ [1,n], ∀FDMi,j ≠ 0 PMi,j = FDMi,j/Ti  Expressivity can be regarded as a mechanism that displays transmission and interpretation vividness of feelings and emotions. For example fear in front of a threat. Physical factors interfere like cardiac rhythm, changes in respiratory system, in endocrine system, in muscular system, in circulatory system, secretion of neurotransmitters, etc. Another important factor is empathy which is the capacity of feelings and emotions recognition in others [6]. It is out of our research to explain how these physical changes are made or how empathy takes place among living beings. We just simulate expressivity in music generation. We compiled 10 melodies, 5 of them generated by our model and another 5 by human composers and we asked human subjects to rank melodies according to whether they liked them or not, with numbers between 1 and 10 being number 1 the most they liked. None of subjects knew about the order of music compositions. These 10 melodies were presented as in Table I. We presented this test to more than 30 participants in different places and events. We sought that the characteristics of these participants were as varied as possible (age, gender and education), however most of them come from a related IT background. Test results were encouraging, since automatically generated melodies were ranked at 3rd and 4th place above human compositions. Table II shows the ranking of melodies as a result of the Turing-like test we developed

@@

>>>>

Пристапот опишан во \cite{GarciaSalas2011} може наједонставно да се објасни како n-gram модел или модел со Маркови синџири. Системот се состои од дел за учење и дел за копонирање. Делот за учење генерира правила врз основа на податочното множество, а делот за компонирање генерира нова музика врз основа на правилата и има повратна врска кон делот за учење. Правилата се изразени преку 3 матрици: матрица на времетраења на нотите, локална матрица на фрекфенции и кумулативна матрица на фрекфенции. Овие матрици се пополнуваат според n-gram фрекфенции на појавување во податочното множество. Алгоритамот за генерирање пресметува матрица на веројатност на појавување како функција од претходно споменатите матрици. Генерирањето се врши со стохастичен процес врз основа на матрицата на веројатности.

Голем број на алгоритми и техники измислени дури од самите почетоци на истражување на полето на машинско учење, како што се модели со невронски мрежи, машини со носечки вектори, дрва на одлука и сл., во минатото не покажува многу добри резултати во однос рачно изградени експертски модели. Најголемо ограничување беа пресметковната моќ и меморискиот капацитет на машините на коишто се извршуваа истите, влијаејќи на големината и комплексноста на моделите за машинско учење како и количината на податоци што може да се обработи при учење на истите. Меѓутоа во последните десетина години започнаа да се користат графичките акцелератори (попознати како графички картички), дотогаш највеќе користени за видео игри, за општа намена (GPGPU - General Purpouse GPU). Се појавија на сцена две библиотеки CUDA од NVIDIA Corp. и OpenCL - слободен софтвер развиен од заедницата на корисници, кои овозможуваат користење на графичките акцелератори за секакви пресметковни намени, што се покажа многу корисно за развивање на модели за машинско учење. Оттокаш се појави и експлозивен интерес за изстражување на секакви теми и решавање на секакви проблеми со користење машинско учење, вклучувајќи и модели за компјутерско генерирање на музика. Самото зголемување на пресметковна моќ овозможува создавање на многу подлабок, пософистициран и поапстрактен систем од тоа што го нудеа претходно споменатите техники. Во продолжение следуа преглед на повеќе пристапи за генерирање на музика со длабоко учење, кое претставува подмножество на техники за машинско учење со користење на длабоки невронски мрежи.

@@

 \cite{GarciaSalas2011} Во трудот е опишана и евалуација на резултатите во стил на Турингов тест, на 30 учесници од различна возраст и познавање на музика, но поголем дел од ИТ индустрија, им биле пуштени 10 песни, 5 генеирани од човек, а 5 од алгоритмот, кои ги рангирале по тоа колку им се допаѓаат. Две од генерираните песни биле рангирани на позиција 3 и 4.
